Outbreak response models of vaccine-preventable diseases in humans (1970-2019) - A systematic review (Supplementary Files)

### 2023-06-19 analyses/scripts/orv_sys_rev_supplementary.Rmd
Shortened the no-fmd data object name

compact_data_with_citation_keys_no_fmd <- compact_data_with_citation_keys %>% filter(disease != 'fmd') 
```
```{r echo=FALSE}
#' Count by collaboration types and make a bar plot
collab_types_count <- compact_data_no_fmd %>%
    count(author_affiliation_type, sort = TRUE) %>% 
    mutate(author_affiliation_type = as_factor(author_affiliation_type))

@@

countries_studied_by_count <- compact_data_with_citation_keys_no_fmd %>% 
    separate_rows(country_studied, sep = ' ') %>%
    distinct(title, country_studied, .keep_all = TRUE) %>% 
    count(collab_type, country_studied, name = 'num_of_studies', sort = T)

@@

compact_data_with_citation_keys_no_fmd <- compact_data_with_citation_keys %>% filter(disease != 'fmd') 
```

@@

## Citations of studies during 2009-2011
```{r echo=FALSE}
#Citation table of studies during 2009-2011 (Peak period)
studies_in_2009_2011_df <- compact_data_with_citation_keys_no_fmd %>%
  separate_rows(disease, sep = ' ') %>% 
  filter(publication_year >= 2009, publication_year <= 2011) %>%
  arrange(disease) %>%
  select(title, publication_year, disease, objectives, bibtexkey) %>% 
  mutate(disease = str_replace(disease, ' ', ' and '))

@@

## Citation table of studies during 2015-2016 per disease and objective type (Peak period)
```{r echo=FALSE}
studies_between_2015_2016_df <- compact_data_with_citation_keys_no_fmd %>%
  separate_rows(disease, sep = ' ') %>% 
  filter(publication_year >= 2015, publication_year <= 2016) %>%
  arrange(disease, publication_year) %>%
  select(title, publication_year, disease, objectives, bibtexkey) %>% 
  mutate(disease = str_replace(disease, ' ', ' and '))

@@

## Citation table of studies in 2019 (Peak period)
```{r echo=FALSE}
studies_in_2019_df <- compact_data_with_citation_keys_no_fmd %>%
  filter(publication_year == 2019) %>%
  arrange(disease) %>%
  select(title, publication_year, disease, objectives, bibtexkey) %>% 
  mutate(disease = str_replace(disease, ' ', ' and '))

>>>>

compact_data_with_citation_keys_no_fmd <- compact_data_with_citation_keys %>% filter(disease != 'fmd') 
```
```{r echo=FALSE}
#' Count by collaboration types and make a bar plot
collab_types_count <- data_without_fmd %>%
    count(author_affiliation_type, sort = TRUE) %>% 
    mutate(author_affiliation_type = as_factor(author_affiliation_type))

@@

countries_studied_by_count <- data_without_fmd %>% 
    separate_rows(country_studied, sep = ' ') %>%
    distinct(title, country_studied, .keep_all = TRUE) %>% 
    count(collab_type, country_studied, name = 'num_of_studies', sort = T)

@@

data_without_fmd <- compact_data_with_citation_keys %>% filter(disease != 'fmd') 
```

@@

## Citations of studies during 2009-2011
```{r echo=FALSE}
#Citation table of studies during 2009-2011 (Peak period)
studies_in_2009_2011_df <- data_without_fmd %>%
  separate_rows(disease, sep = ' ') %>% 
  filter(publication_year >= 2009, publication_year <= 2011) %>%
  arrange(disease) %>%
  select(title, publication_year, disease, objectives, bibtexkey) %>% 
  mutate(disease = str_replace(disease, ' ', ' and '))

@@

## Citation table of studies during 2015-2016 per disease and objective type (Peak period)
```{r echo=FALSE}
studies_between_2015_2016_df <- data_without_fmd %>%
  separate_rows(disease, sep = ' ') %>% 
  filter(publication_year >= 2015, publication_year <= 2016) %>%
  arrange(disease, publication_year) %>%
  select(title, publication_year, disease, objectives, bibtexkey) %>% 
  mutate(disease = str_replace(disease, ' ', ' and '))

@@

## Citation table of studies in 2019 (Peak period)
```{r echo=FALSE}
studies_in_2019_df <- data_without_fmd %>%
  filter(publication_year == 2019) %>%
  arrange(disease) %>%
  select(title, publication_year, disease, objectives, bibtexkey) %>% 
  mutate(disease = str_replace(disease, ' ', ' and '))
